### 2017-01-23 thesis/intro/intro.tex
Minor edit in intro and methods

@@

In the following chapter, the detailed methods of all the analyses carried out for this project is outlined.
The results from these analyses are split into two parts, each presented in separate chapters: first part of the results clarify the relationship between the obesity associated genetic signatures with various cancer types; and the second part of the results consist of the links between the pathway associated genetic signatures and various cancer types, as well as the previously identified obesity associated signatures.
\\

\noindent
(By the end of this thesis, the aim presented here will be answered with clarity.
However, it is without doubt that there will be many more questions to be answered than what was actually answered -- those questions shall remain unanswered for future investigations.)
include this bit or not \ldots

>>>>

One thing to note here is that most of these pathway associated genetic signatures are involved in one or more of the Hallmarks of Cancer.
This means that these pathway associated signatures can be used to provide insights into the underlying biological mechanisms of the samples used in this project.

@@

\section{Thesis outline}
\label{sec:thesis_outline}

In the following chapter, the detailed methods of all the analyses carried out for this project is outlined.
The results from these analyses are split into two parts, each presented in separate chapters: first part of the results clarify the relationship between the obesity associated genetic signatures with various cancer types; and the second part of the results consist of the links between the pathway associated genetic signatures and various cancer types, as well as the previously identified obesity associated signatures.
By the end of this thesis, the aim presented here will be answered with clarity.

### 2017-01-23 thesis/methods/methods.tex
Started editing introduction -- tmp commit
Minor edit in intro and methods

@@

Heatmaps were created using either the \texttt{heatmap.2} function from \textit{gplots} package, or the \texttt{heatmap.2x} function written by Tom Kelly.
All of the heatmaps that required no or one column bar used the \texttt{heatmap.2} function, and all of the heatmaps that required more than one column bars used the \texttt{heatmap.2x} function.

>>>>

\subsection{Box and scatter plots}
\label{sub:box_and_scatter_plots}

Box plots and scatter plots were used to visualise the association of a metagene with some of the clinical variables of the data.
Box plots and scatter plots were plotted using the \texttt{boxplot} and \texttt{plot} functions from the \textit{graphics} package in \gls{r}, respectively.
The p-value and \gls{anova} p-value in the box plots were calculated using the \texttt{t.test} and \texttt{aov} functions from the \textit{stats} package in \gls{r}, respectively.
The line of best fit and the $R^2$-value of the line were taken from the summary statistics produced by the \texttt{lm} function from the \textit{stats} package in \gls{r}.

@@

To visualise the association of the sample metagene scores with the sample gene expression, heatmaps were used.
Heatmap is an effective method to visualise such data, as the ordering of the genes and/or samples may be controlled based on certain values, for example metagene scores.
Furthermore, heatmaps are able to cluster the samples and/or genes based on the ``distance'' between the data, or in other words, how closely related the data are.
Heatmaps were created using the \texttt{heatmap.2} function from the \textit{gplots} package in \gls{r}.
